---
title: "milk_yield_and_robot_functionality"
author: "Thomas FitzGerald"
date: "2023-05-04"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(plotly)
library(ggplot2)

library(stringr)
library(lubridate)
```

Data Import
```{r}
df.1 <- read.csv('C:\\Users\\Thoma\\OneDrive\\Desktop\\Farm_1\\HISTORY - Milking ALL.csv')

df.1 <- df.1 %>% mutate(Date.1 = as.Date(Date.Time, format = "%m/%d/%Y"))
df.1 <- df.1 %>% mutate(Date.2 = as.Date(Date.Time, format = "%Y-%m-%d"))
df.1 <- df.1 %>% mutate(Date = case_when(
  is.na(Date.1) ~ Date.2,
  is.na(Date.2) ~ Date.1))

df.1$Milk.Yield.Dif <- df.1$Milk.Yield.Expected - df.1$Milk.Yield

#Takes formatted milking data
df.2 <- read.csv('C:\\Users\\Thoma\\OneDrive\\Desktop\\Farm_2\\test_out_merged.csv')
df.2 <- df.2 %>% mutate(Date = as.Date(Date, format = "%m/%d/%Y"))
#df.2$Milk.Yield.Dif <- df.2$Milk.Yield.Expected - df.2$Milk.Yield
```

```{r}
df.1.grouped <- 
  subset(df.1,!is.na(Milk.Yield)) %>% #This should maybe be converting to 0 instead.  I _think_ they are all non-milking rows, though.
  group_by(Date) %>%
  summarise('Mean_Milk_Yield' = mean(Milk.Yield))

df.1.grouped
#Farm 1 Plot
plot_ly(df.1.grouped, x = ~Date) %>%
  add_trace(y = ~Mean_Milk_Yield, type= 'scatter', mode='lines') %>%
  add_trace(x = as.Date("2022-11-11"), y=c(31,35), type='scatter', mode='lines') %>%
  add_trace(x = as.Date("2022-12-16"), y=c(31,35), type='scatter', mode='lines') %>%
  add_trace(x = as.Date("2023-01-04"), y=c(31,35), type='scatter', mode='lines') %>%
  add_trace(x = as.Date("2023-02-14"), y=c(31,35), type='scatter', mode='lines')
```

```{r}
colnames(df.2)
```
LF,LR,RF,RR Incomplete, Kickoff, Not_Milked_Teats are our measurements for 'Robot Malfunction'.  Let's broadly group everything by date, then do an lm to check for relationships:

```{r}
#Time_In_Area,Consumed ommitted

df.2.grouped <- df.2 %>%
  subset(Event_Type=='Milking') %>% #This should maybe be converting to 0 instead.  I _think_ they are all non-milking rows, though.
  select(Date,Animal_Number,Milking_Station_Number,Total_Conductivity,Milk_Yield,
         Duration,Milking_Interval,
         LF_Kickoff,LR_Kickoff,RF_Kickoff,RR_Kickoff,
        LF_Incomplete,LR_Incomplete,RF_Incomplete,RR_Incomplete,
         LF_Not_Milked_Teats,LR_Not_Milked_Teats,RF_Not_Milked_Teats,RR_Not_Milked_Teats) %>%
  mutate(count = 1,
              LF_Kickoff=LF_Kickoff=="True",
              LR_Kickoff=LR_Kickoff=="True",
              RF_Kickoff=RF_Kickoff=="True",
              RR_Kickoff=RR_Kickoff=="True",
              LF_Incomplete=LF_Incomplete=="True",
              LR_Incomplete=LR_Incomplete=="True",
              RF_Incomplete=RF_Incomplete=="True",
              RR_Incomplete=RR_Incomplete=="True",
              LF_Not_Milked_Teats=LF_Not_Milked_Teats=="True",
              LR_Not_Milked_Teats=LR_Not_Milked_Teats=="True",
              RF_Not_Milked_Teats=RF_Not_Milked_Teats=="True",
              RR_Not_Milked_Teats=RR_Not_Milked_Teats=="True",) %>%
group_by(Date) %>%
summarise('Count' = sum(count),
          'Kickoff_Sum' = sum(LF_Kickoff,LR_Kickoff,RF_Kickoff,RR_Kickoff),
          'Incomplete_Sum' = sum(LF_Incomplete,LR_Incomplete,RF_Incomplete,RR_Incomplete),
         'Not_Milked_Sum' = sum(LF_Not_Milked_Teats,LR_Not_Milked_Teats,RF_Not_Milked_Teats,RR_Not_Milked_Teats),
         'Total_Milk_Yield' = sum(Milk_Yield),
         'Mean_Milk_Yield' = mean(Milk_Yield),
         'Mean_Conductivity' = mean(Total_Conductivity),
         'Mean_Duration' = mean(Duration))

df.2.grouped
```
```{r}
lm.obj <- lm(data=df.2.grouped,Total_Milk_Yield~.)
summary(lm.obj)
```
The strongest relationships to total milk yield are count and mean (no surprise).  Incomplete and Not Milked have little relation to total, but kickoff seems more strongly related.

Now, let's check Correlations to Total Milk Yield
```{r}
print('Count')
cor(df.2.grouped$Total_Milk_Yield,df.2.grouped$Count)
print('Kickoff')
cor(df.2.grouped$Total_Milk_Yield,df.2.grouped$Kickoff_Sum)
print('Incomplete')
cor(df.2.grouped$Total_Milk_Yield,df.2.grouped$Incomplete_Sum)
print('Not Milked')
cor(df.2.grouped$Total_Milk_Yield,df.2.grouped$Not_Milked_Sum)
print('Duration')
cor(df.2.grouped$Total_Milk_Yield,df.2.grouped$Mean_Duration)
```
Count and yield are highly correlated.  Not surprising: more milkings = more milk.  I suspect kickoff, incomplete, and not milked are just highly correlated to count.

If we check the correlation between robot errors (Kickoff,Incomplete,Not_Milked) and count:
```{r}
print('Kickoff')
cor(df.2.grouped$Count,df.2.grouped$Kickoff_Sum)
print('Incomplete')
cor(df.2.grouped$Count,df.2.grouped$Incomplete_Sum)
print('Not Milked')
cor(df.2.grouped$Count,df.2.grouped$Not_Milked_Sum)
print('Duration')
cor(df.2.grouped$Count,df.2.grouped$Mean_Duration)
```
High or extremely high correlations.  Oddly, kickoff is not as strongly correlated with count as the other two.


```{r}
  plot_ly(df.2.grouped,x=~Date,y=~Count)
  plot_ly(df.2.grouped,x=~Date,y=~Total_Milk_Yield)
  plot_ly(df.2.grouped,x=~Count,y=~Total_Milk_Yield)
```
Machine functionality:
```{r}
  plot_ly(df.2.grouped,x=~Date,y=~Kickoff_Sum)
  plot_ly(df.2.grouped,x=~Date,y=~Incomplete_Sum)
  plot_ly(df.2.grouped,x=~Date,y=~Not_Milked_Sum)
  plot_ly(df.2.grouped,x=~Date,y=~Mean_Duration)
```
```{r}
plot_ly(subset(df.2.grouped,,x=~Date,y=~Kickoff_Sum))
```


Yield stats:
```{r}
  plot_ly(df.2.grouped,x=~Date,y=~Mean_Milk_Yield)
  plot_ly(df.2.grouped,x=~Date,y=~Mean_Conductivity)
```



From the above, we have a few avenues to explore.  

First, last week's tests using mean milk yield should've been using total milk yield, so we need to re-test those.  
Secondly, something besides milking count is influencing kickoff that does not influence incomplete/not milked.  We should check kickoff.
Third, conductivity seems to peak May-September, then drop off.  None of the other metrics have this time trend.  May be worth looking at.


For re-testing, let's look at last weeks function:
```{r}
#Debug
df <- df.2.animal.group
variable.name <- 'Total_Milk_Yield'
date.of.change <- '2022-12-14'
i <- 1

over_time_change <- function(df,variable.name,date.of.change){
  date.of.change <- as.Date(date.of.change)
  results = data.frame(matrix(ncol=5,nrow=0))
  colnames(results) <- c('days_from_change','p_value','dif','before_val','after_val')
  for(i in 1:7){
    before.date <- as.Date(date.of.change) - i
    after.date <- as.Date(date.of.change) + i
    before.values <- subset(df, Date < date.of.change & Date >= before.date)[variable.name]
    after.values <- subset(df, Date > date.of.change & Date <= after.date)[variable.name]
    single.results <- t.test(before.values,after.values)
    results[i,] <- list(i,
                  single.results$p.value,
                  single.results$estimate[1]-single.results$estimate[2],
                  single.results$estimate[1],
                  single.results$estimate[2])
  }
  return(results)
}
```
I see a major issue with this.  We're looking at a distribution of milkings, not of milk production.  We really need to group by animal before testing milk yield.

First, we re-configure our data for testing total milk production per animal (instead of milk return per milking):
```{r}
df.2.animal.group <- df.2 %>%
  subset(Event_Type=='Milking') %>% #This should maybe be converting to 0 instead.  I _think_ they are all non-milking rows, though.
  select(Date,Animal_Number,Total_Conductivity,Milk_Yield) %>%
  mutate(Milking_Count=1) %>%
  group_by(Date,Animal_Number) %>% 
  summarise('Milking_Count' = sum(Milking_Count),
        'Total_Milk_Yield' = sum(Milk_Yield),
         'Mean_Milk_Yield' = mean(Milk_Yield),
         'Mean_Conductivity' = mean(Total_Conductivity))

df.2.animal.group
```

```{r}
over_time_change(df.2.animal.group,'Total_Milk_Yield','2022-11-11')
over_time_change(df.2.animal.group,'Total_Milk_Yield','2022-11-30')
over_time_change(df.2.animal.group,'Total_Milk_Yield','2022-12-14')
over_time_change(df.2.animal.group,'Total_Milk_Yield','2023-02-01')
```
Looking at the above, 12/14 had the most noticeable and consistent change in overall milk production, starting at 2 days and peaking at 4.

Let's do some sanity checks:
```{r}
over_time_change(df.2.animal.group,'Total_Milk_Yield','2022-11-20')
over_time_change(df.2.animal.group,'Total_Milk_Yield','2022-12-03')
over_time_change(df.2.animal.group,'Total_Milk_Yield','2022-12-25')
over_time_change(df.2.animal.group,'Total_Milk_Yield','2023-01-15')
```


```{r}
df <- df.2.animal.group
variable.name <- 'Total_Milk_Yield'
date.of.change <- '2022-12-14'
i <- 4

  before.date <- as.Date(date.of.change) - i
  after.date <- as.Date(date.of.change) + i
  before.values <- subset(df, Date < date.of.change & Date >= before.date)[variable.name]
  after.values <- subset(df, Date > date.of.change & Date <= after.date)[variable.name]

df <- rbind(
  cbind(before.values,type='Before'),
  cbind(after.values,type='After')
)
  
  
df %>%
  plot_ly(type='violin') %>%
  add_trace(
    x = ~type[df$type == 'Before'],
    y = ~Total_Milk_Yield[df$type == 'Before'],
    legendgroup = 'Before',
    scalegroup = 'Before',
    name = 'Before',
    side = 'negative',
    box = list(
      visible = T
    ),
    meanline = list(
      visible = T
    ),
    color = I("blue")
  ) %>%
    add_trace(
    x = ~type[df$type == 'After'],
    y = ~Total_Milk_Yield[df$type == 'After'],
    legendgroup = 'After',
    scalegroup = 'After',
    name = 'After',
    side = 'positive',
    box = list(
      visible = T
    ),
    meanline = list(
      visible = T
    ),
    color = I("red")
  ) %>%
  layout(
    xaxis = list(
      title = ""  
    ),
    yaxis = list(
      title = "",
      zeroline = F
    ),
    violingap = 0,
    violingroupgap = 0,
    violinmode = 'overlay'
  )
```


```{r}
df.2.grouped.by.machine <- df.2 %>%
  subset(Event_Type=='Milking') %>% #This should maybe be converting to 0 instead.  I _think_ they are all non-milking rows, though.
  select(Date,Animal_Number,Milking_Station_Number,Total_Conductivity,Milk_Yield,
         Duration,Milking_Interval,
         LF_Kickoff,LR_Kickoff,RF_Kickoff,RR_Kickoff,
        LF_Incomplete,LR_Incomplete,RF_Incomplete,RR_Incomplete,
         LF_Not_Milked_Teats,LR_Not_Milked_Teats,RF_Not_Milked_Teats,RR_Not_Milked_Teats) %>%
  mutate(count = 1,
              LF_Kickoff=LF_Kickoff=="True",
              LR_Kickoff=LR_Kickoff=="True",
              RF_Kickoff=RF_Kickoff=="True",
              RR_Kickoff=RR_Kickoff=="True",
              LF_Incomplete=LF_Incomplete=="True",
              LR_Incomplete=LR_Incomplete=="True",
              RF_Incomplete=RF_Incomplete=="True",
              RR_Incomplete=RR_Incomplete=="True",
              LF_Not_Milked_Teats=LF_Not_Milked_Teats=="True",
              LR_Not_Milked_Teats=LR_Not_Milked_Teats=="True",
              RF_Not_Milked_Teats=RF_Not_Milked_Teats=="True",
              RR_Not_Milked_Teats=RR_Not_Milked_Teats=="True",) %>%
group_by(Date,Milking_Station_Number) %>%
summarise('Count' = sum(count),
          'Kickoff_Sum' = sum(LF_Kickoff,LR_Kickoff,RF_Kickoff,RR_Kickoff),
          'Incomplete_Sum' = sum(LF_Incomplete,LR_Incomplete,RF_Incomplete,RR_Incomplete),
         'Not_Milked_Sum' = sum(LF_Not_Milked_Teats,LR_Not_Milked_Teats,RF_Not_Milked_Teats,RR_Not_Milked_Teats),
         'Total_Milk_Yield' = sum(Milk_Yield),
         'Mean_Milk_Yield' = mean(Milk_Yield),
         'Mean_Conductivity' = mean(Total_Conductivity),
         'Mean_Duration' = mean(Duration))

df.2.grouped.by.machine
```

```{r}
df.2.grouped.by.machine$Milking_Station_Number <- as.character(df.2.grouped.by.machine$Milking_Station_Number)

df <- subset(df.2.grouped.by.machine,Milking_Station_Number==1)
cor(df$Count,df$Total_Milk_Yield)
cor(df$Kickoff_Sum,df$Total_Milk_Yield)
sum(df$Total_Milk_Yield)
df <- subset(df.2.grouped.by.machine,Milking_Station_Number==2)
cor(df$Count,df$Total_Milk_Yield)
cor(df$Kickoff_Sum,df$Total_Milk_Yield)
sum(df$Total_Milk_Yield)
df <- subset(df.2.grouped.by.machine,Milking_Station_Number==3)
cor(df$Count,df$Total_Milk_Yield)
cor(df$Kickoff_Sum,df$Total_Milk_Yield)
sum(df$Total_Milk_Yield)
```

```{r}
plot_ly(df.2.grouped.by.machine,x=~Date,y=~Kickoff_Sum, color=~Milking_Station_Number)
plot_ly(df.2.grouped.by.machine,x=~Date,y=~Total_Milk_Yield, color=~Milking_Station_Number)
```

```{r}
df.2.grouped.by.animal <- df.2 %>%
  subset(Event_Type=='Milking') %>% #This should maybe be converting to 0 instead.  I _think_ they are all non-milking rows, though.
  select(Date,Animal_Number,Milking_Station_Number,Total_Conductivity,Milk_Yield,
         Duration,Milking_Interval,
         LF_Kickoff,LR_Kickoff,RF_Kickoff,RR_Kickoff,
        LF_Incomplete,LR_Incomplete,RF_Incomplete,RR_Incomplete,
         LF_Not_Milked_Teats,LR_Not_Milked_Teats,RF_Not_Milked_Teats,RR_Not_Milked_Teats) %>%
  mutate(count = 1,
              LF_Kickoff=LF_Kickoff=="True",
              LR_Kickoff=LR_Kickoff=="True",
              RF_Kickoff=RF_Kickoff=="True",
              RR_Kickoff=RR_Kickoff=="True",
              LF_Incomplete=LF_Incomplete=="True",
              LR_Incomplete=LR_Incomplete=="True",
              RF_Incomplete=RF_Incomplete=="True",
              RR_Incomplete=RR_Incomplete=="True",
              LF_Not_Milked_Teats=LF_Not_Milked_Teats=="True",
              LR_Not_Milked_Teats=LR_Not_Milked_Teats=="True",
              RF_Not_Milked_Teats=RF_Not_Milked_Teats=="True",
              RR_Not_Milked_Teats=RR_Not_Milked_Teats=="True",) %>%
group_by(Date,Animal_Number) %>%
summarise('Count' = sum(count),
          'Kickoff_Sum' = sum(LF_Kickoff,LR_Kickoff,RF_Kickoff,RR_Kickoff),
          'Incomplete_Sum' = sum(LF_Incomplete,LR_Incomplete,RF_Incomplete,RR_Incomplete),
         'Not_Milked_Sum' = sum(LF_Not_Milked_Teats,LR_Not_Milked_Teats,RF_Not_Milked_Teats,RR_Not_Milked_Teats),
         'Total_Milk_Yield' = sum(Milk_Yield),
         'Mean_Milk_Yield' = mean(Milk_Yield),
         'Mean_Conductivity' = mean(Total_Conductivity),
         'Mean_Duration' = mean(Duration))

df.2.grouped.by.animal
```

```{r}
df.2.grouped.by.animal$Milking_Station_Number <- as.character(df.2.grouped.by.animal$Animal_Number)
lm.obj <- lm(data=df.2.grouped.by.animal,Total_Milk_Yield~Animal_Number)
summary(lm.obj)

```

```{r}
plot_ly(df.2.grouped.by.machine,x=~Date,y=~Kickoff_Sum, color=~Milking_Station_Number)
plot_ly(df.2.grouped.by.machine,x=~Date,y=~Total_Milk_Yield, color=~Milking_Station_Number)
```